# Reproducible Research: Peer Assessment 1
```{r echo=FALSE, results='hide'}
saved.locale <- Sys.getlocale("LC_TIME")
Sys.setlocale("LC_TIME", "C")
```

## Loading and preprocessing the data
```{r}
data <- read.table(unz('activity.zip'
                   , 'activity.csv')
                   , header = TRUE
                   , sep = ","
                   , stringsAsFactors=F
                   , colClasses = c('integer', 'Date', 'integer')
                   )
```


## What is mean total number of steps taken per day?
```{r}
steps.per.day <- tapply(data$steps, data$date, sum, na.rm=T)
hist(steps.per.day, main='total number of steps taken each day', xlab='steps per day')
```
There is the mean total number of steps taken per day: `r sprintf("%8.2f", mean(steps.per.day, na.rm =T))`.
There is the median total number of steps taken per day: `r median(steps.per.day, na.rm =T)`.


## What is the average daily activity pattern?
```{r}
steps.per.interval <- aggregate(data$steps, by=list(data$interval), FUN=mean, na.rm=T)
plot(steps.per.interval$x, type='l')

max.interval <- which.max(steps.per.interval$x)

```

The 5-minute interval, on average across all the days in the dataset,
contains the maximum number of steps: `r max.interval`-th, this one:  `r steps.per.interval$Group[max.interval]`.

Devise a strategy for filling in all of the missing values in the dataset. The
strategy does not need to be sophisticated. For example, you could use
the mean/median for that day, or the mean for that 5-minute interval, etc.
## Imputing missing values
There were `r sum(is.na(data$steps))` NA values.

```{r}
rounded.value.for.interval <- function(interval) {
  round(steps.per.interval$x[steps.per.interval$Group.1 == interval])
}

data.tidy <- data
data.tidy$steps[is.na(data$steps)] <- sapply(data$interval[is.na(data$steps)], rounded.value.for.interval)
```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
steps.per.day.tidy <- aggregate(c(data.tidy$steps) , by=list(data.tidy$date), FUN=sum)
names(steps.per.day.tidy) <- c('date', 'steps')
hist(steps.per.day.tidy$steps, main='total number of steps taken each day', xlab='steps per day')

```
There is the mean total number of steps taken per day: `r sprintf("%8.2f", mean(steps.per.day.tidy))`.
There is the median total number of steps taken per day: `r sprintf("%8.0f", median(steps.per.day.tidy))`.

What is the impact of imputing missing data on the estimates of the total
daily number of steps?
```{r}
steps.per.day.tidy$weekdays <- factor(c(
  ifelse(weekdays(steps.per.day.tidy$date) == 'Sunday' | weekdays(steps.per.day.tidy$date) == 'Saturday'
    , 'weekend'
    , 'weekday')
  ))
```

```{r echo=FALSE, results='hide'}
Sys.setlocale("LC_TIME", saved.locale)
Sys.setlocale("LC_TIME", "Russian_Russia.1251") # remove this
```




